Initialisation de la gestion forestière, PNR du Massif des Bauges

### 2021-07-19 13cd_Initialisation_gestion_all.Rmd
Updated description

>>>>

```{r iti.salem, echo=FALSE, warning=FALSE, message=FALSE, fig.height = 5}
tab.typo.salem <- lapply(l.forestStands, function(x){aggregate(AREA/10000 ~ FOREST_TYPE_CODE + itineraire + DOMAINE_TYPE, data = x, FUN = function(x){sum(x, na.rm = TRUE)})})
tab.typo.salem <- mapply(function(x, y){x$scenario <- y;return(x)}, tab.typo.salem, as.list(liste.scenario), SIMPLIFY = FALSE)
tab.typo.salem <- do.call(rbind, tab.typo.salem)
names(tab.typo.salem)[3] <- "Surface"
```
